Robust Estimation, Prediction and Control with \\ Linear Dynamics and Generic Costs

### 2020-02-04 main.tex
Add table of results for the driving task
Update figures

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{img/epc-friction}
	\caption{\textbf{Left}: the state prediction procedure. \textbf{Right}: the model estimation procedure.}
	\label{fig:estimation-prediction}
\end{figure}

@@

\begin{table}[htbp]
	\caption{Performances on the Obstacle task}
	\label{tab:obstacle}
	\centering
	\begin{tabular}{lccc}
		\toprule
		\multirow{2}{*}{Agent} &
		\multicolumn{2}{c}{Return} &
		\multirow{2}{*}{Failures} \\
		\cmidrule{2-3} & min &
		mean $\pm$ std & \\
		\midrule
		Oracle & {11.6} & {$14.2 \pm 1.3$} & 0\% \\
		\midrule
		{Nominal} & {2.8} & \textbf{$13.8 \pm 2.0$} & {4\%} \\
		Robust & \textbf{10.4} & {$13.0 \pm 1.5$} & \textbf{0\%} \\
		\bottomrule
	\end{tabular}
\end{table}

\begin{figure}[tp]
	\centering
	\includegraphics[width=0.8\linewidth]{img/regret.pdf}
	\caption{The mean regret with its $95\%$ confidence interval for the robust and nominal agents with respect to time.}
	\label{fig:regret}
\end{figure}

@@

\begin{table}[htbp]
	\caption{Performances on the Driving task}
	\label{tab:driving}
	\centering
	\begin{tabular}{lccc}
		\toprule
		\multirow{2}{*}{Agent} &
		\multicolumn{2}{c}{Return} &
		\multirow{2}{*}{Failures} \\
		\cmidrule{2-3} & min &
		mean $\pm$ std & \\
		\midrule
		Oracle & {6.9} & {7.4} & 0\% \\
		\midrule
		{Nominal K} & {3.8} & \textbf{4.6} \\
		{Nominal U} & {3.0} & {4.3} \\
		Robust & {3.04} & {13.0} & \textbf{0\%} \\
		\bottomrule
	\end{tabular}
\end{table}

>>>>

\begin{figure}[t]
	\centering
	\includegraphics[width=0.6\linewidth]{img/ellipsoid}
	\caption{The model estimation procedure. The size of the confidence region $C_{[N],\delta}$ shrinks with the number of samples $N$.}
\end{figure}

\begin{figure}[t]
	\centering
	\includegraphics[width=0.8\linewidth]{img/obstacle_small}
	\caption{The state prediction procedure. At each timestep (red to green), we bound the set of reachable states considering model uncertainty \eqref{eq:confidence}}
	\label{fig:estimation-prediction}
\end{figure}

@@

\begin{table}[htbp]
	\caption{Performances on the Obstacle task}
	\label{tab:obstacle}
	\centering
	\begin{tabular}{lccc}
		\toprule
		\multirow{2}{*}{Agent} &
		\multirow{2}{*}{Failures} &
		\multicolumn{2}{c}{Return} \\
		\cmidrule{3-4} & & min &
		mean $\pm$ std \\
		\midrule
		Oracle & 0\% & {11.6} & {$14.2 \pm 1.3$} \\
		\midrule
		{Nominal} & {4\%} & {2.8} & \textbf{$\mathbf{13.8} \pm 2.0$} \\
		Robust (ours) & \textbf{0\%} & \textbf{10.4} & {$13.0 \pm 1.5$} \\
		\bottomrule
	\end{tabular}
\end{table}

\begin{figure}[tp]
	\centering
	\includegraphics[width=0.8\linewidth]{img/regret.pdf}
	\caption{The mean regret with its $95\%$ confidence interval for the robust and nominal agents with respect to the number $N$ of samples.}
	\label{fig:regret}
\end{figure}

@@

\begin{table}[htbp]
	\caption{Performances on the Driving task}
	\label{tab:driving}
	\centering
	\begin{tabular}{lccc}
		\toprule
		\multirow{2}{*}{Agent} &
		\multirow{2}{*}{Failures} &
		\multicolumn{2}{c}{Return} \\
		\cmidrule{3-4} && min &
		mean $\pm$ std  \\
		\midrule
		Oracle & 0\% & {6.9} & $7.4 \pm 0.5$ \\
		\midrule
		{Nominal B} & 4\% & {5.2} & $\mathbf{7.3} \pm 1.5$ \\
		{Nominal R} & 33\% & {3.5} & $6.4 \pm 0.26$ \\
		Robust (ours) & \textbf{0\%} & \textbf{6.8} & $7.1 \pm 0.29$ \\
		\bottomrule
	\end{tabular}
\end{table}
